Clustering of Last.fm Music

### 2015-05-07 writeup/MSDgroupwriteup.tex

In building a recommendation system, we had to take into account various trade-offs in the type of models we chose to fit. For example, some methods take more information about the user and the song into account (e.g. metadata) while others use a collaborative filtering approach without taking into account user or song characteristic such as age, genre, location, etc.
There is no set similarity measure between two songs, as evident by the fact that songs by the same artist are often very different. As such, there are many different types of algorithms to explore.

>>>>

In building a recommendation system, we had to take into account various trade-offs in the type of models we chose to fit. For example, some methods take more information about the user and the song into account (i.e. content-based) while others use a collaborative filtering approach without taking into account user or song characteristics such as age, genre, location, etc.
There is no set similarity measure between two songs, as evident by the fact that songs by the same artist are often very different. As such, there are many different types of algorithms to explore.
